\normalfont{A bird's-eye view on the habitability of exoplanets via statistical learning techniques}

### 2020-09-30 Manuscript/Manuscript.tex
PUB

The first approach that was considered is the classification decision tree: as we can see from Fig \ref{DecisionTree} the main discriminant is the stellar luminosity: this feature discriminate,as one expects, the largest part of the habitable planet from the non-habitable. The nodes $4$, $9$ and $19$ discriminates deeply the habitability on the basis of stellar temperature planet temperature and its main distance from the host star. Note that the mean distance (P\_D) has a less importance: this can be ascribed to the fact that the habitability was extended beyond the "earth zone" by considering habitable planets that, with a particular atmosphere as shown in fig \ref{Planets_habitability_Seager}, have the correct surface temperature for liquid water. 
\footnote{In principle one may wonder if a better approach should considered only the planets like Earth habitable or perhaps to distinguish the two cases in order to get the distance effect: the issue here is that these exoplanets are very few, thus to preserve the significance of the habitable planets, if such approach was undertaken, a further reduction of the dataset had to be considered. Since this choice strongly limits the quality of forecasts, such approach was not considered.}. The performance of this algorithm on this dataset, evaluated with a 10-fold cross-validation, is reported in Fig \ref{Decision_tree_performances} and in the table \ref{DecisionTree_perf_tab}

@@

>>>>

The first approach that was considered is the classification decision tree: as we can see from Fig \ref{DecisionTree} the main discriminant is the stellar luminosity: this feature discriminate,as one expects, the largest part of the habitable planet from the non-habitable. The nodes $4$, $9$ and $19$ discriminates deeply the habitability on the basis of stellar temperature planet temperature and its main distance from the host star. Note that the mean distance (P\_D) has a less importance: this can be ascribed to the fact that the habitability was extended beyond the "earth zone" by considering habitable planets that, with a particular atmosphere as shown in fig \ref{Planets_habitability_Seager}, have the correct surface temperature for liquid water. 
\footnote{In principle one may wonder if a better approach should considered only the planets like Earth habitable or perhaps to distinguish the two cases in order to get the distance effect: the issue here is that these exoplanets are very few, thus to preserve the significance of the habitable planets, if such approach was undertaken, a further reduction of the dataset had to be considered. Since this choice strongly limits the quality of forecasts, such approach was not considered.}. The performance of this algorithm on this dataset, evaluated with a 10-fold cross-validation, is reported in Fig \ref{Decision_tree_performances} and in the table \ref{DecisionTree_perf_tab}. Next the random forest approach was considered.First consider the plot in Fig. \ref{Random_forest_trees}: at first when the number of trees is moved is increased the error for

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.8\textwidth]{Pic/Random_forest_trees.pdf}
\caption{}
\label{Random_forest_trees}
\end{center}
\end{figure}
